\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\title{Module Plan}
\author{Tavish Mankash}
\date{}
\begin{document}
\maketitle
\small
\section*{Overview}
Short, practical breakdown of the codebase. Each module has a small, clear contract so we can iterate fast.

\section*{Modules}
\subsection*{1. data}
Purpose: get terrain into memory.
\begin{itemize}
  \item \texttt{load\_synthetic\_terrain(shape)}: quick, deterministic heightmap (for dev/testing).
  \item \textit{(later)} \texttt{load\_laz(path)}: read LAZ/point cloud and return gridded heightmap.
  \item Inputs: file path or shape; Outputs: \(H\in\mathbb{R}^{m\times n}\) height grid.
\end{itemize}

\subsection*{2. preprocess}
Purpose: convert raw points to a usable grid; light smoothing if needed.
\begin{itemize}
  \item \textit{(placeholder)} \texttt{voxelize(points, voxel\_size)}.
  \item Inputs: point cloud; Outputs: grid/voxels.
\end{itemize}

\subsection*{3. graph}
Purpose: neighbors and distances for grid search.
\begin{itemize}
  \item \texttt{iter\_neighbors(idx, shape, connectivity)}: valid 4/8-neighbors.
  \item \texttt{step\_distance(a,b)}: 1 or \(\sqrt{2}\) for diagonals.
  \item Inputs: grid index; Outputs: neighbor indices and base step cost.
\end{itemize}

\subsection*{4. cost}
Purpose: movement cost + heuristic.
\begin{itemize}
  \item \texttt{slope\_cost(H,a,b; k,p)}: penalize slope as in the design doc (tan-based penalty).
  \item \texttt{heuristic\_euclidean(a,b)}: admissible planar distance.
  \item Inputs: height grid, two cells; Outputs: scalar costs.
\end{itemize}

\subsection*{5. planner}
Purpose: path search.
\begin{itemize}
  \item \texttt{a\_star(start, goal, neighbors, h, move\_cost)}: generic A*.
  \item Inputs: start/goal, callbacks; Outputs: path (list of cells), cost.
\end{itemize}

\subsection*{6. cli}
Purpose: quick demo and smoke tests.
\begin{itemize}
  \item \texttt{python -m terrain\_navigate}: runs a small demo on synthetic terrain.
  \item Flags: \texttt{--size}, \texttt{--k}, \texttt{--p}.
\end{itemize}

\section*{Notes}
Keep functions small and testable. Prefer simple numpy-only ops first; add heavier deps only when needed.

\end{document}
